\chapter{Enquête}%
\label{ch:Enquête}

\section{Rexx vs Python comparative study - success criteria}
I'm doing a comparative study between Rexx and Python. I'll be comparing both within the context of a couple of use cases.
A few use cases that I have in mind, these are not set in stone (feel free to email me at vincent.gielen@student.hogent.be if you have other suggestions/feedback):
(1) IPL an LPAR (Rexx is favored); (2) Use API's (Python is favored); (3) Generate JCL (using Pythin Jinja2 vs Rexx File Tailoring Services); (4) Using RACF (details TBD)

\subsection{Feel free to share your personal information (name, role, company, ...). This is not mandatory.}
Enter your answer...

\subsection{How long have you been working on Mainframes?}
\begin{itemize}
    \item Less than 5 years
    \item Between 5 and 10 years
    \item Between 10 and 25 years
    \item More than 25 years
\end{itemize}

\subsection{What is your experience level with Python (on z/OS)?}
\begin{itemize}
    \item Beginner
    \item Intermediate
    \item Advanced
    \item Expert
\end{itemize}

\subsection{What is your experience level with Rexx?}
\begin{itemize}
    \item Beginner
    \item Intermediate
    \item Advanced
    \item Expert
\end{itemize}

\subsection{When comparing Python and Rexx, what are some requirements that you feel could be used? In other words, what (objective or subjective) criteria can be used to properly compare both? Some examples are (1) dependencies on external libraries or (2) lines of code, ...}
Enter your answer...

\subsection{Feel free to give any sort of comments, feedback, ... that can help me with my thesis.}
Enter your answer...